Properties of Winning Iterated Prisoner's Dilemma Strategies.

### 2020-04-15 paper/perfomances_table.tex
checks that notebooks run

\begin{tabular}{lllllllll}
\toprule
{} &                     Name & \$\textbackslash bar\{r\}\$ &                   Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
\midrule
0  &            Evolved HMM 5 &   0.00667 &                 Grumpy &    0.1402 &          Fortress4 &   0.01266 &           Alternator &    0.3037 \\
1  &           Evolved FSM 16 &   0.00995 &                    \$e\$ &   0.19388 &           Defector &   0.01429 &               \$\textbackslash phi\$ &   0.30978 \\
2  &     EvolvedLookerUp2\_2\_2 &   0.01064 &         Tit For 2 Tats &   0.20617 &  Better and Better &   0.01587 &                  \$e\$ &    0.3125 \\
3  &  Evolved FSM 16 Noise 05 &   0.01667 &  Slow Tit For Two Tats &   0.20962 &    Tricky Defector &   0.01875 &                \$\textbackslash pi\$ &   0.31686 \\
4  &        PSO Gambler 2\_2\_2 &   0.02143 &           Cycle Hunter &   0.21538 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
5  &              Evolved ANN &   0.02878 &         Risky QLearner &   0.22222 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
6  &            Evolved ANN 5 &    0.0339 &            Retaliate 3 &   0.22887 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
7  &        PSO Gambler 1\_1\_1 &   0.03704 &          Cycler CCCCCD &   0.23507 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
8  &            Evolved FSM 4 &   0.04891 &            Retaliate 2 &   0.23913 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
9  &         PSO Gambler Mem1 &   0.05036 &        Defector Hunter &   0.24038 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
10 &                 Winner12 &   0.06011 &              Retaliate &   0.24177 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
11 &             Fool Me Once &    0.0614 &    Hard Tit For 2 Tats &      0.25 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
12 &                      DBS &   0.07143 &               ShortMem &   0.25286 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
13 &            DoubleCrosser &     0.072 &    Limited Retaliate 3 &   0.25316 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
14 &              BackStabber &   0.07519 &      Limited Retaliate &   0.25706 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{lllllllllllll}
\toprule
{} &                     Name & \$\textbackslash bar\{r\}\$ &                   Name & \$\textbackslash bar\{r\}\$ &                        Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
\midrule
0  &            Evolved HMM 5 &     0.007 &                 Grumpy &      0.14 &                         DBS &         0 &          Fortress4 &     0.013 &             Evolved FSM 16 &         0 &           Alternator &     0.304 \\
1  &           Evolved FSM 16 &      0.01 &                    \$e\$ &      0.19 &     Evolved FSM 16 Noise 05 &     0.008 &           Defector &     0.014 &    Evolved FSM 16 Noise 05 &     0.013 &               \$\textbackslash phi\$ &      0.31 \\
2  &     EvolvedLookerUp2\_2\_2 &     0.011 &         Tit For 2 Tats &     0.206 &      Evolved ANN 5 Noise 05 &     0.013 &  Better and Better &     0.016 &                       MEM2 &     0.027 &                  \$e\$ &     0.312 \\
3  &  Evolved FSM 16 Noise 05 &     0.017 &  Slow Tit For Two Tats &      0.21 &                 BackStabber &     0.024 &    Tricky Defector &     0.019 &              Evolved HMM 5 &     0.043 &                \$\textbackslash pi\$ &     0.317 \\
4  &        PSO Gambler 2\_2\_2 &     0.022 &           Cycle Hunter &     0.215 &               DoubleCrosser &     0.025 &          Fortress3 &     0.022 &       EvolvedLookerUp2\_2\_2 &     0.049 &    Limited Retaliate &     0.353 \\
5  &              Evolved ANN &     0.029 &         Risky QLearner &     0.222 &               Evolved ANN 5 &     0.028 &     Gradual Killer &     0.025 &       Spiteful Tit For Tat &     0.059 &     Anti Tit For Tat &     0.354 \\
6  &            Evolved ANN 5 &     0.034 &          Cycler CCCCCD &     0.229 &                 Evolved ANN &     0.038 &         Aggravater &     0.028 &           Nice Meta Winner &     0.069 &  Limited Retaliate 3 &     0.356 \\
7  &        PSO Gambler 1\_1\_1 &     0.037 &            Retaliate 3 &      0.23 &        Spiteful Tit For Tat &     0.051 &             Raider &     0.031 &         NMWE Finite Memory &     0.069 &          Retaliate 3 &     0.356 \\
8  &            Evolved FSM 4 &     0.049 &            Retaliate 2 &     0.239 &               Evolved HMM 5 &     0.051 &         Cycler DDC &     0.045 &         NMWE Deterministic &      0.07 &            Retaliate &     0.357 \\
9  &         PSO Gambler Mem1 &      0.05 &        Defector Hunter &      0.24 &              Level Punisher &     0.052 &        Hard Prober &     0.051 &                    Grudger &      0.07 &          Retaliate 2 &     0.358 \\
10 &                 Winner12 &      0.06 &              Retaliate &     0.242 &                   Omega TFT &     0.059 &         SolutionB1 &      0.06 &           NMWE Long Memory &     0.074 &  Limited Retaliate 2 &     0.361 \\
11 &             Fool Me Once &     0.061 &    Hard Tit For 2 Tats &      0.25 &                Fool Me Once &     0.059 &      Meta Minority &     0.061 &  Nice Meta Winner Ensemble &     0.076 &             Hopeless &     0.368 \\
12 &                      DBS &     0.071 &      Arrogant QLearner &      0.25 &  PSO Gambler 2\_2\_2 Noise 05 &     0.067 &              Bully &     0.061 &       EvolvedLookerUp1\_1\_1 &     0.077 &    Arrogant QLearner &     0.406 \\
13 &            DoubleCrosser &     0.072 &    Limited Retaliate 3 &     0.253 &              Evolved FSM 16 &     0.078 &             EasyGo &     0.071 &            NMWE Memory One &      0.08 &    Cautious QLearner &     0.409 \\
14 &              BackStabber &     0.075 &               ShortMem &     0.253 &                  EugineNier &      0.08 &    Fool Me Forever &     0.071 &            NMWE Stochastic &     0.085 &      Fool Me Forever &     0.418 \\
\bottomrule
\end{tabular}
